%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% 
%% Taolun Chai's resume
%%   - based off work by Michael DeCorte 
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%



%%
%% The following code sets up the document formatting
%%


%this assumes that res_yy.sty is in some path
\documentstyle[hyperref, margin, line, multicol]{res_yy}

\hypersetup{backref,pdfpagemode=Full,colorlinks=true,backref}

\addtolength{\oddsidemargin}{-0.45in}
\addtolength{\voffset}{-0.30in}
\addtolength{\textwidth}{1.00in} \addtolength{\textheight}{1.50in}

\renewcommand{\namefont}{\LARGE\emph}



%%
%% The following code defines some macros for terms which have raised font
%% (ie 4\fourth would result 4th with the 'th' raised (superscripted)
%%

\def\Cplusplus{{\rm C\raise.5ex\hbox{\small ++}}}
\def\CSharp{{\rm C\raise.5ex\hbox{\small \#}}}
% 'st' 'nd' 'rd' 'th' superscripts for numbers
\def\first{{\raise.5ex\hbox{\small st}}}
\def\second{{\raise.5ex\hbox{\small nd}}}
\def\third{{\raise.5ex\hbox{\small rd}}}
\def\fourth{{\raise.5ex\hbox{\small th}}}



%%
%% starting the actual document
%%

\begin{document}

%the name in big fonts at the top of resume
%this is left aligned
\name{Taolun Chai}

%this is right aligned
\address{
Address: 556 main st, Apt 104, New York, NY. \ \ \ \ Tel: (414)-530-4932 \ \ \ \ \ E-mail: tc1112@nyu.edu  
}

\begin{resume}



%%
%% This section of code is inelegant, but I'm too lazy to fix it
%%

\section{\textsc{Education:}}

\textbf{\newline New York University} \hfill 2010 - Present \\
Master Student in Computer Science \hfill Expected: May, 2012
\newline
\textbf{Southern Polytechnic State Unversity} \hfill 2008 - 2010 \\ 
Bachelor of Science in Computer Science \hfill Graduated with Honors
\newline
\textbf{Northeast Normal University} \hfill 2006 - 2010 \\
Bachelor of Science in Computer Science \hfill Graduated

%%\section{\textsc{Technical Skills}}
%%\textbf{Programming Languages: } Java, C/C++, SQL, Python, Perl \\
%%\textbf{Operating System: } Linux, Mac OS X, Windows \\
%%\textbf{Application: } VIM, Eclipse, Git, SVN, Apache, GDB \\
%%\textbf{Database: } mysql, SQL Server
%%\newline

\section{\textsc{Course Work:}}

\begin{multicols}{2}
\begin{itemize}
    \item Algorithm
    \item Programming Languages
    \item Open Source Tools
    \item Operating System
    \item Financial Computing 
    \item Distribute Computing
\end{itemize}
\end{multicols}


\section{\textsc{Qualifications:}}

\textbf{\newline Programming Languages}: \Cplusplus, Java, C, \CSharp, Python, Perl, SQL \\
\textbf{Editors and Tools}: Vim, GCC, GDB, MySQL, Microsoft Visual Studio, CMake, \LaTeX \\
\textbf{Version Control System}: Git, SVN \\
\textbf{Operating System}: Linux, Mac OS X, Windows 
%%
%% the meat of the resume starts now
%%


\section{\textsc{Work Experience:}}
\textbf{\newline Shutterstock Images LLC} \hfill Software Engineer Intern\\
Development Environment: C/C++, Perl on Linux \hfill Summer 2011
\begin{itemize}
    \item Designed and implemented a customized Photo anlysis library for automatic detect and recognize given arbitrary image.
    \item Based on the library, designed and implemented the prototype of image search and auto key-wording system.
    \item Helped updating search engine of freestock.com.
\end{itemize}

%Designed and implemented a customized Photo anlysis library for automatic detect and recognize given arbitrary image.
%Based on the library, designed and implemented the prototype of image search and auto key-wording system. \\
%Also helped replacing the search engine of www.freestock.com.

\textbf{Southern Polytechnic State University} \hfill Research Assistant\\
Development Environment: \CSharp, matlab on Windows \hfill Spring 2009 through Spring 2010 \\
Focused on pattern recognition research. Published "An improvement on the
modified gradient method for face localization" on IEEE Southeast-Con 2010
and presented a lecture on the conference. \\
Participated then led the FaceTrace project, which apply face recognition
technology on identify person for access control purpose.
Helped delivered the distributed version on time.
Designed and implemented the hand-held version system.

\section{\textsc{Other Projects:}}
\textbf{\newline On-line Java Instant Assessment System} \hfill Spring 2010\\
Applied the Unit test idea on automatically collect and grading assignments. Utilized by professors at SPSU serving all level Java programming course. \\
Published "Design of Online Runtime and Testing Environment for Instant Java Programming Assessment" on 2010 7th International Conference on Information Technology.

\textbf{Web-based Ontology for Vulnerability Management} \hfill Fall 2009\\
By analyzing the holistic vulnerability information with given security requirements, 
provides a quantitative score for the evaluated software product.\\
Offers recommendation on software vulnerability control to achieve ISA $($Information
Security Automation$)$.

%%
%% This section could also use more formatting, but looks ok, as is
%%


\section{\textsc{Activities:}} 
\textbf{\newline}
SPSU Honor’s Student. \\
Member of Alpha (National College Honor Scholarship Society).  \\
SPSU Computer Science Departement Dean's List.\\
First Prize of ACM/ICPC 2008 Northeast China Part Region Site.	\\
First Prize of ACM/ICPC 2008 Jilin Region Site. 

%%
%% Nothing special here, just a normal table
%%




\end{resume}
\end{document}
